Algebraic File Synchronization: Adequacy and Completeness

### 2018-02-27 p2/ordering.tex
Review
Merged definitions

We recognize that mulitple orders may be possible;
let us therefore describe our ordering algorithm by
defining a subset of the permutations, $\ordersetsign$.
The simplicity of the definition means that enumerating
all sequences in $\ordersetsign$ can be implemented by a straightforward
algorithm.

As we will see, $\ordersetsign$ generates all possible
sequences of commands that do not break all filesystems.
In \cref{simple_reorder_equiv}, we offer a formal proof of this.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.

\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parentf{m}$, then $[y]=[\vald]$
\item if $\parentf{n}=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

To prove \cref{simple_reorder_equiv}, we need the following results.

@@

TODO MOVE TO AMONG THE AXIOMS TO AVOID DUPLICATION.
BUT THIS NEEDS THE DEFINITION OF SIMPLE SEQUENCES.

\begin{proof}
% BACK_TO_THE_FS TODO
% TODO APPENDIX
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

>>>>

As we recognize that mulitple orders may be possible,
let us describe our ordering algorithm by
defining a subset of the permutations, $\ordersetsign$.
The simplicity of the definition means that enumerating
all sequences in $\ordersetsign$ can be implemented by a straightforward
algorithm.

As we will see, $\ordersetsign$ contains all possible
sequences of commands that do not break all filesystems.
In \cref{simple_reorder_equiv}, we offer a formal proof of this.
The facts that all valid reorderings of simple sequences are equivalent,
and all equivalent sequences are reorderings are important 
properties of simple sequences.

\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of 
permutations of the commands in $S$
for which the following holds:
for any subsequence $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parentf{m}$, then $[y]=[\vald]$
\item if $\parentf{n}=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

To prove \cref{simple_reorder_equiv}, we need the following simple results.

@@

\begin{proof}
% BACK_TO_THE_FS TODO
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

### 2018-02-27 p2/upd-def.tex
Merged definitions

The set of commands $U$ necessary to transform $\FS$ into $\FS_1$ can be collected
by inspecting the union of non-empty nodes in the two filesystems.
If at node $n$, $\FS(n)=x$ and $\FS_1(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $U$.
We can always do so as there is a command available for all combinations of input and output types and values.
We see that any suitable $U$ necessarily contains commands on all nodes that have changed.

@@

\begin{mydef}[Minimal sets or sequences]
A sequence or set of commands is minimal if it contains at most one command on each node.
\end{mydef}

\begin{mydef}[Simple sets or sequences]
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

>>>>

The set of commands $U$ necessary to transform $\FS$ into $\FS_1$ can be collected
by inspecting the union of non-empty nodes in the two filesystems.
If at node $n$, $\FS(n)=x$ and $\FS_1(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $U$.
We can always do so as there is a command available for all combinations of input and output types and values.
We see that any suitable $U$ necessarily contains commands on all nodes at which the values have changed.

@@

\begin{mydef}[Minimal and simple command sets and command sequences]
A sequence or set of commands is \emph{minimal} if it contains at most one command on each node.
It is \emph{simple} if it is minimal and it does not contain assertion commands.
\end{mydef}
